Simulate Desert Ant Behaviour

### 2011-12-11 doc/paper.tex
working on doc

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{subfig}
\usepackage{amssymb, amsmath}
\usepackage{hyperref}
\usepackage[framed,numbered,autolinebreaks,useliterate]{mcode}

@@

\title{Simulate Desert Ant Behaviour}
\author{Georg Wiedebach, Wolf Vollprecht}
%\date{date}

@@

% IMPORTANT
% you MUST include the ETH declaration of originality here; it is available for download on the course website or at http://www.ethz.ch/faculty/exams/plagiarism/index_EN; it can be printed as pdf and should be filled out in handwriting

@@

We chose to limit our landscape: We implemented fixed boundaries, which hinder the ant from escaping out of our experiment area. This is important to limit the time the ant needs to find food and thus making our simulation very less time-consuming. A matrix stores information about taken and free points by the values true or false, where false stand for an obstacle. Nest, feeder, landmarks and local vectors are saved separately as vectors, to make them easy to reach.

\subsubsection*{Ant}
Our ant should follow certain, simple rules to move according to the studies we received as part of the project description. Such are basic rules like avoiding obstacles or a little more specific rules like following the global vector when returning to the nest and using the local vectors of the landmarks when finding the food again. During the simulation and after the ant has had success in finding food our local vectors should as well change according to the new found and better path.

@@

@@

\subsubsection{move} 
The move method is heart of the ant class: it accepts any general direction vector as input and sets the new position of the ant as a result. A general direction input can be calculated in the method “find food” or “return to nest”. It also handles all the checking for obstacles. Move is invoked in every time-step. Because the ant has only a choice of 8 possible next positions the method must calculate a new direction vector to one of the first order Moore neighbours:

@@

\subsection{Simulation}
The simulation class main purpose is to serve as a holder for the landscape and the ant. It also handles everything that has to do with output. The most important functions are the run-method, and the render-method, these two are described below.
\subsubsection{Run}
In this method there are basically two while-loops checking whether the ant is searching for food or trying to return to the nest. This is indicated by two Boolean values in the class ant. In each cases the corresponding ant-methods are invoked. Here is a simple example of using parts of the run-method (pseudo code):
\begin{lstlisting}
while the ant has no food
	search for food and move one step
	if the simulation needs to be rendered
		render the actual position of the ant on the map
	end
end
\end{lstlisting}

@@

\section{References}

@@

>>>>

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{subfig}
\usepackage{amssymb, amsmath}
\usepackage{hyperref}
\usepackage{pdfpages}
\usepackage[framed,numbered,autolinebreaks,useliterate]{mcode}

@@

\title{Simulate Desert Ant Behaviour}
\author{Georg Wiedebach, Wolf Vollprecht}
\date{date}

@@

\includepdf{images/confirmation_en.pdf}
% IMPORTANT
% you MUST include the ETH declaration of originality here; it is available for download on the course website or at http://www.ethz.ch/faculty/exams/plagiarism/index_EN; it can be printed as pdf and should be filled out in handwriting

@@

We chose to limit our landscape: We implemented fixed boundaries, which hinder the ant from escaping out of our experiment area. This is important to limit the time the ant needs to find food and thus making our simulation very less time-consuming. A matrix stores information about taken and free points by the values true or false, where false stand for an obstacle. Nest, feeder, landmarks and local vectors are saved separately as vectors, to make them easy to reach.
\begin{figure}[h!]
	\centering
 	\includegraphics[scale=0.6]{images/landscape.jpg}
 	\caption{Example of a simple landscape: obstacles red, feeder and nest are indicated with x and o}
\end{figure}
\subsubsection*{Ant}
Our ant should follow certain, simple rules to move according to the studies we received as part of the project description. Such are basic rules like avoiding obstacles or a little more specific rules like following the global vector when returning to the nest and using the local vectors of the landmarks when finding the food again. During the simulation and after the ant has had success in finding food our local vectors should as well change according to the new found and better path.

@@

\begin{figure}[h!]
	\centering
	\subfloat[Original image]{\includegraphics[scale=0.4]{images/map2skal.png}}
	\subfloat[Generated landscape]{\includegraphics[scale=0.5]{images/map2.jpg}}
	\caption[Generating a map from image]{Generated map from image}
\end{figure}

@@

\subsubsection{Move} 
The move method is heart of the ant class: it accepts any general direction vector as input and sets the new position of the ant as a result. A general direction input can be calculated in the method “find food” or “return to nest”. It also handles all the checking for obstacles. Move is invoked in every time-step. Because the ant has only a choice of 8 possible next positions the method must calculate a new direction vector to one of the first order Moore neighbours:

@@

\begin{figure}[h!]
	\centering
	\subfloat[Without second direction]{\includegraphics[scale=0.5]{images/mainvec.jpg}} \hspace*{1cm}
	\subfloat[With second direction]{\includegraphics[scale=0.5]{images/secvec.jpg}}
	\caption[Comparison: Using second direction or not]{Calculating move direction with and without second direction}
\end{figure}
\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.6]{images/foodsearch.jpg}
	\caption[Ants first search for food]{First search for food. No local vectors are set.}
\end{figure}
\subsection{Simulation}
The simulation class main purpose is to serve as a holder for the landscape and the ant. It also handles everything that has to do with output. The most important functions are the run-method, and the render-method, these two are described below.
\subsubsection{Run}
In this method there are basically two while-loops checking whether the ant is searching for food or trying to return to the nest. This is indicated by two Boolean values in the class ant. In each cases the corresponding ant-methods are invoked. Here is a simple example of using parts of the run-method (pseudo code):
\begin{lstlisting}
while the ant has no food
	search for food and move one step
	if the simulation needs to be rendered
		render the actual position of the ant on the map
	end
end
\end{lstlisting}

@@

\newpage
\section{References}

@@

\listoffigures
